--- 
title: "Dissertation Defense"
author: "Kirk Gosik"
date: "`r Sys.Date()`"
setspace: doublespacing
linestretch: 2
lof: yes
lot: yes
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---


Where does this text go if i put it before

# Abstract {-}

Knowledge about how changes in gene expression are encoded by expression quantitative trait loci (eQTLs) is a key to construct the genotype-phenotype map for complex traits or diseases. Traditional eQTL mapping is to associate one transcript with a single marker at a time, thereby limiting our inference about a complete picture of the genetic architecture of gene expression. Here, I present an innovative application of variable selection approaches to systematically detect main effects and interaction effects among all possible loci on differentiation and function of gene expression. Forward-selection-based procedures were particularly implemented to tackle complex covariance structures of gene-gene interactions. We reanalyzed a published genetic and genomic dataset collected in a mapping population of Caenorhabditis elegans, gaining new discoveries on the genetic origin of gene expression differentiation, which could not be detected by a traditional one-locus/one-transcript analysis approach.

**Update**
  (This is from Han Hao's proposal, update for yours)
  
In this proposal, we focus on developing computational frameworks for QTL
mapping in different types of functional valued traits. In Chapter 2, we deal with
the situation where the trait values follow a parametric trend. A Richard curve is
used to model plant height growth, and QTLs are examined for their association
with the onset, offset and duration of the developmentaol process. In Chapter 3, the
trait values do not have a specific mathematical form. The shape of leaf is modelled
in a nonparametric way, and QTLs are examined for their association with shape
development. In Chapter 4, we study the interaction between two functional valued
traits. The growth of two interacting traits is modelled with a differential equation
system, and QTLs are examined for their association with the type and intensity
of such interaction.

```{r eval=FALSE}
devtools::install_github("rstudio/bookdown")
```


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
